\textbf{NBA Party}

### 2017-05-02 init_model.rnw
Now using logged  for party variable. Only helps significance, and doesn't hurt betting.

<<>>=
HOURS <- 24
lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, nmusicians, 0)]
@

@@

<<echo=-1>>=
load(file = 'tmp_data/covers_lines_mlb.RData')
lines[, party := ifelse(team != location & weekend == 1, nmusicians, 0)]

>>>>

<<>>=
HOURS <- 24
lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, log(nmusicians), 0)]
@

@@

<<echo=-1>>=
load(file = 'tmp_data/covers_lines_mlb.RData')
lines[, party := ifelse(team != location & weekend == 1, log(nmusicians), 0)]
